[Standartox](http://standartox.uni-landau.de)

### 2019-08-30 talk/talk43.Rmd
changes

- Arrive in freshwater systems
  - Pharmaceuticals
  - Pesticides
  - Personal care products
  - ...
]

@@

Bernhardt et al. 2017
<img src="/home/scharmueller/Projects/etox-base/talk/data/bernhardt_et_al_chem.png" width="260px">

@@

---
background-image: url(/home/scharmueller/Projects/etox-base/talk/data/stream.jpg)
background-size: 375px
background-position: 90% 50%

@@

- Regulatory thresholds

@@

--
<br><br><br><br>
### Toxicity Data?

@@

<img src="/home/scharmueller/Projects/etox-base/talk/data/organigram2.png" width="850px" style="position:absolute; left:10px; top:130px;">

@@

  - Prepares ecotoxicological test data + additional data

@@

```{r fig.width=10, fig.height=7, echo=FALSE, warning=FALSE, message=FALSE}
gg_comparison = readRDS(file.path(datadir_tk, 'gg_oncor_mykiss_standartox_output.rds'))
gg_comparison
```

@@

```{r fig.width=10, fig.height=7, echo=FALSE, warning=FALSE, message=FALSE}
gg_comparison = readRDS(file.path(datadir_tk, 'gg_oncor_mykiss_standartox_ppdb_comparison.rds'))
gg_comparison
```

@@

- standartox::
  - Application Programming Interface (API)
  - scriptable
  - __reproducible__

@@

standartox(cas = '52-68-6',
           endpoint = 'EC50',
           effect = 'MOR',
           duration = c(48, 96),
           taxon = 'Oncorhynchus',
           filtered = TRUE,
           aggregated = TRUE)
```

@@

<img src="http://3.bp.blogspot.com/-Wpp0vCJQDHo/U_ZMorXEynI/AAAAAAAAA7Y/Y-f-3brn99k/s1600/GBIF_logo_short_form.gif" width="120px" style="position:absolute; bottom:20px; left:70px;">

>>>>

- Arrive in freshwater systems
  - Pharmaceuticals
  - Pesticides
  - Personal care products
  - ...

### Effect?
]

@@

Bernhardt et al. 2017
<img src="/home/scharmueller/Projects/etox-base/talk/data/bernhardt_et_al_chem.png" width="300px">

@@

---
background-image: url(/home/scharmueller/Projects/etox-base/talk/data/stream.jpg)
background-size: 400px
background-position: 90% 50%

@@

.pull-left[
- Regulatory thresholds

@@

<br>
### Toxicity Data?
]

@@

<img src="/home/scharmueller/Projects/etox-base/talk/data/organigram2.png" width="950px" style="position:absolute; left:10px; top:130px;">

@@

@@

```{r fig.width=11, fig.height=7, echo=FALSE, warning=FALSE, message=FALSE}
gg_comparison = readRDS(file.path(datadir_tk, 'gg_oncor_mykiss_standartox_output.rds'))
gg_comparison
```

@@

```{r fig.width=11, fig.height=7, echo=FALSE, warning=FALSE, message=FALSE}
gg_comparison = readRDS(file.path(datadir_tk, 'gg_oncor_mykiss_standartox_ppdb_comparison.rds'))
gg_comparison
```

@@

- standartox::
  - Application Programming Interface (API)
  - Scriptable
  - __Reproducible__

@@

standartox(cas = '52-68-6',
           endpoint = 'EC50',
           effect = 'MOR',
           duration = c(48, 96),
           taxon = 'Oncorhynchus mykiss')
```

@@

<img src="http://3.bp.blogspot.com/-Wpp0vCJQDHo/U_ZMorXEynI/AAAAAAAAA7Y/Y-f-3brn99k/s1600/GBIF_logo_short_form.gif" width="100px" style="position:absolute; bottom:20px; left:70px;">
